Turbulence in compact to giant H~II regions

### 2023-04-18 strucfunc_paper.tex
More tweaks to Orion section

\citet{arthur2016turbulence} calculated the structure function of different emission lines in the inner Orion Nebula with varying degrees of ionization. 
They found that higher ionization lines show a larger velocity dispersion
and a steeper structure function slope. 
They also make a comparison with previous work (see Table~5 on their paper), finding a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
The work by \citet{arthur2016turbulence} is the only one that has calculated the structure function for the \ha{} emission line, for this reason it will be the only one that we use for comparison.
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [\ion{O}{3}] emission lines and for [\ion{S}{2}] and [\ion{N}{2}] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\).
For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07 \pm 0.03}, a correlation length of \SI{0.068 \pm 0.004}{pc} and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\). 
The difference with respect to this last value is due to the fact that \citet{arthur2016turbulence} masked areas with high values of centroid velocity (see Figure~2 on their paper).
Since they are based on the same observational data,
the differences of order 30\% between their results and our own
are entirely due to the different methodologies employed.

>>>>

\citet{arthur2016turbulence} calculated the structure function of different emission lines in the inner Orion Nebula with varying degrees of ionization. 
They found that higher ionization lines show a larger velocity dispersion
and a steeper structure function slope. 
They also make a comparison with previous work (see Table~5 on their paper), finding a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
% The work by \citet{arthur2016turbulence} is the only one that includes the \ha{} emission line,
% for this reason it will be the only one that we use for comparison.
The power-law index obtained by \citet{arthur2016turbulence} is \(m \sim 1.17 \pm 0.08\) for \halpha,
% and [\ion{O}{3}] emission lines and for [\ion{S}{2}] and [\ion{N}{2}] they found \(m \sim 0.8 \pm 0.1\). 
with a correlation length of \SI{\sim 0.05}{pc} and velocity variance
\(\sigma\pos^2= \SI{9.4}{km^{2 }.s^{-2}}\).
This compares with our own values of
% For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of 
\(m = 1.07 \pm 0.03\), \(r_0 = \SI{0.068 \pm 0.004}{pc}\)
and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\). 
Since they are based on the same observational data,
the differences of order 30\% between the \citet{arthur2016turbulence}
results and our own are entirely due to the different methodologies employed.
In the case of \(\sigma\pos^2\), their value is lower than ours since
they masked out the locations of known high-velocity Herbig-Haro flows, whereas we do not.
